\documentclass[a4paper]{article}

\usepackage{geometry}
\geometry{left=1.5cm, right=1.5cm, top=2.54cm, bottom=2.54cm}
\usepackage{graphicx, hyperref, setspace, amsmath, amssymb, titlesec, fancyhdr, multicol, parskip, indentfirst, etoolbox, caption, cite, xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}

\titleformat{\section}{\centering\large\scshape}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{1em}{}
\setstretch{1.0} 
\setlength{\parskip}{6pt} 
\titlespacing{\section}{0pt}{6pt}{6pt}
\titlespacing{\subsection}{0pt}{6pt}{6pt}
\titlespacing{\subsubsection}{0pt}{6pt}{6pt}

\title{Real-Time Localization Framework for Autonomous Basketball Robots}

\date{} 
\captionsetup{labelfont={small,sc}, textfont={small,sc}}

\renewcommand{\thesection}{\Roman{section}.}
\renewcommand{\thesubsection}{\textit{\Alph{subsection}.}}
\renewcommand{\thesubsubsection}{\textit{\arabic{subsubsection}.}}
\renewcommand{\thetable}{\Roman{table}} 
\renewcommand{\thefigure}{\Roman{figure}} 

\titleformat{\subsection}{\normalfont\large\itshape}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\itshape}{\thesubsubsection}{1em}{}


\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    \noindent\rule{\textwidth}{1pt}\par
    \vspace{0.3em}
    {\LARGE \bfseries \@title \par}
    \vspace{0.3em}
    \noindent\rule{\textwidth}{1pt}\par
  \end{center}
}
\makeatother

\begin{document}

\maketitle
\vspace{1cm}


\begin{multicols}{2}
    \centering
    \textbf{Naren Medarametla}\\
    \textit{School of Computer Science Engineering}\\
    \textit{Vellore Institute of Technology}\\
    \textit{Chennai, India}\\
    \texttt{naren.medarametla2023@vitstudent.ac.in}
    \vfill\null

    \columnbreak

    \textbf{Sreejon Mondal}\\
    \textit{School of Electrical and Electronics Engineering}\\
    \textit{Vellore Institute of Technology}\\
    \textit{Chennai, India}\\
    \texttt{sreejon.mondal2023@vitstudent.ac.in}
    \vfill\null
\end{multicols}

\singlespacing
\setlength{\parskip}{6pt}
\setlength{\parindent}{0.5cm}

\begin{multicols}{2}
\setlength{\columnsep}{0.5cm}

\noindent \textbf{\textit{Abstract---}
Localization is a fundamental capability for autonomous robots, enabling them 
to operate effectively in dynamic environments. In Robocon 2025, accurate and 
reliable localization is crucial for improving shooting precision, avoiding 
collisions with other robots, and navigating the competition field efficiently. 
In this paper, we propose a hybrid localization algorithm that integrates classical 
techniques with learning-based methods, relying solely on visual data from the court’s
floor to achieve self-localization on the basketball field.
}

\small	
\noindent \textbf{
  \textit{Keywords---}\textit{Robot Localization, Autonomous Navigation, Neural Networks, Robocon}}

\section{Introduction}
\textbf{Section II} reviews existing methods and prior research related to this work. 
\textbf{Section III} provides a detailed description of our proposed algorithm, approach, and model architecture. 
\textbf{Section IV} provides the results obtained from our experiments. 
\textbf{Section V} evaluates the accuracy of our approach and discusses potential directions for future work.

\section{Related Work}
\section{Methodology}
Our approach is a two-step process that begins with \textbf{Preprocessing} the image,
followed by passing it to the model for \textbf{Inference}.
\subsection{Preprocessing}
The input image is converted from the RGB color space to the HSV color space, then the white regions are masked out using two predefined HSV ranges.
The image is downsampled through a radial scan, flattened, and finally passed through the neural network.

% add diagram here of flowchart
% also add labels in the paragarphs pointing to images and algorithms like figure a, etc
\begin{algorithm}[H]
\caption{Downsampling}
\begin{algorithmic}[1]
\Statex \textbf{Input: }Image
\State $H \gets$ Image.height
\State $W \gets$ Image.width
\State $R \gets$ Black Image
\For{angle $\gets$ 0 to 180 step 2}
    \State $lastPixel \gets 0$
    \State $cx \gets \text{H / 2}$
    \State $cy \gets \text{W}$
    \For{d $\gets$ 0 to max(H, W)}
        \State $x \gets cx + d \times \cos(angle)$
        \State $y \gets cy - d \times \sin(angle)$
        \If{$0 \leq x < \text{W} \ \textbf{and} \ 0 \leq y < \text{H}$}
          \State $pixel \gets Image[y][x]$
          \If{lastPixel = 255 and pixel $\neq$ 255}
            \State $R[y][x] \gets 255 $ 
          \EndIf
          \State $lastPixel \gets pixel$
        \EndIf
    \EndFor
\EndFor
\State \textbf{Return} R
\end{algorithmic}
\end{algorithm}
\section{Results and Analysis}

\section{Conclusion and Future Work}

\section{References}

\end{multicols}

\end{document}